IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
cowl done

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, COWL additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accommodating these
features lies outside the purview of our formalism.

%% \Red{
%% EZY:  This seems like useless detail about the COWL implementation
%% that is not relevant to this paper.
%% 
%% Of course, simply disallowing all external effects for all browsing
%% contexts would break most of the Web.
%% %
%% Hence COWL only enforces IFC, and thus restricts external effects,
%% when the JS code uses the new API.\footnote{
%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
%%   restricting external effects we interpose ``standard''
%%   \texttt{postMessage} communication to ensure that no information is
%%   leaked between contexts that have opted-in and those that have not.
%% }
%% %
%% Moreover, rather than disallowing all external effects, COWL allows
%% controlled network communication by leveraging the fact that web
%% pages already have an accompanying security policy: the same origin
%% policy.
%% %
%% Hence, for example, a worker that has read data only sensitive to
%% \texttt{http://bank.ch} can communicate with this domain; only once
%% \texttt{http://aws.com} data is also included in the context will all
%% network requests be blocked.
%% %
%% Of course, this requires that we use a concrete label format to
%% express the policies; we refer the interested reader to~\tocite{} for
%% more details.}

>>>>

Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, rather than disallowing all external effects, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.
%
While the external effects of COWL can be formally modeled, and indeed
necessary, we do model these effects in our more general framework,
since, like for Node.js case, this is a platform-specific detail.
%
Indeed, the labeled HTTP client semantics of our Node.js
implementation and that of COWL differ, even though they're both
JavaScript systems, simply because of the different settings.
